CO Interlopers Eloping from [C~\textsc{ii}] Surveys

### 2019-03-20 paper/ms.tex
Add correct Fisher matrix simplification

\newcommand{\mynu}[2]{\ensuremath{\nu_{#1,\text{#2}}}}
\newcommand{\denps}{\ensuremath{P_{\delta,\delta}}}
\newcommand{\xps}[2]{\ensuremath{P_{#1,#2}}}
\newcommand{\pstot}[1]{\ensuremath{P_{#1,\text{tot}}}}

@@

\subsection{Something} \label{ssec:co_}
\beq\label{eq:co_fisher}
F_{i,j} = 
\int \frac{\text{d}k\,k^2}{2\pi^2} 
V_{\text{surv}} \sum_{l} \sum_{m} 
\frac{\partial \hat{P}_l(k)}{\partial B_i}
\frac{1}{\Cov{\hat{P}_i(k)}{\hat{P}_j(k)}} 
\frac{\partial \hat{P}_m(k)}{\partial B_j}\text{,}
\eeq
\eeq
\eeq
\eeq

>>>>

\newcommand{\mynu}[2]{\ensuremath{\nu_{#1,\text{#2}}}}
\newcommand{\denps}{\ensuremath{P_{\delta,\delta}}}
\newcommand{\xps}[2]{\ensuremath{P_{#1,#2}}}
\newcommand{\pstot}[1]{\ensuremath{P_{#1,\text{tot}}}}
\newcommand{\Bsum}{\ensuremath{\tilde{B}}}

@@

\subsection{Something} \label{ssec:co_}
We now consider the prospects of measuring the \CO{} transition using a
multi-field approach. First, we choose to label each line with the upper
transitional level, e.g. CO(3-2) is referred to as ``3.'' The relevant Fisher
matrix is then,
\beq\label{eq:co_fisher}
F_{i,j} = 
\int \frac{\text{d}k\,k^2}{2\pi^2} 
V_{\text{surv}} \sum_{l} \sum_{m} 
\frac{\partial \hat{P}_l(k)}{\partial B_i}
\frac{1}{\Cov{\hat{P}_i(k)}{\hat{P}_j(k)}} 
\frac{\partial \hat{P}_m(k)}{\partial B_j}\text{,}
\eeq
where $i$ and $j$ each refer to a line by its upper transitional level and the
$l$ and $m$ sum over all \textit{combinations} of $i$ (or $j$).

However, we can greatly simplify this expression by noticing that in the sum
over $l$ all terms not involving $i$ will vanish in the derivative. Therefore,
if we define the total sum of all bias factors as
\beq\label{eq:sum_bias}
\Bsum = \sum_k B_k\text{,}
\eeq
then we can write the sum portion of Equation~\ref{eq:co_fisher} as,
\beq\label{eq:sum_part_of_fisher}
\sum_l \frac{\partial \hat{P}_l(k)}{\partial B_i}
= (\Bsum - B_i) \denps(k)\text{.}
\eeq
Therefore, we can simplify Equation~\ref{eq:co_fisher} and simply write,
\beq\label{eq:co_fisher_simple}
F_{i,j} = 
\int \frac{\text{d}k\,k^2}{2\pi^2} 
V_{\text{surv}}
\frac{(\Bsum - B_i)(\Bsum - B_j)}
{\Cov{\hat{P}_i(k)}{\hat{P}_j(k)}} \denps(k)^2
\text{.}
\eeq
Interestingly, if one wishes to modify this approach and include the
auto-power spectra in the analysis, the only modification is to make the
substitution $(\Bsum - B_i) \rightarrow (\Bsum + B_i)$, and similarly for $j$.
